Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-07-25 writing/DraftExposurePaper/DraftExposurePaper.Rmd
begin coding countyweather data

```{r}
devtools::install_github("ropenscilabs/rnoaa")
library(rnoaa)
devtools::install_github("leighseverson/countyweather")
library(countyweather)
options("noaakey" = Sys.getenv("noaakey"))
alex_weather <- weather_fips(fips = alex_nldas$fips,
                             date_min = "2010-06-25",
                             date_max = "2010-07-02",
                             var = "PRCP")
```

>>>>

```{r}
#devtools::install_github("ropenscilabs/rnoaa")
library(rnoaa)
#devtools::install_github("leighseverson/countyweather")
library(countyweather)
options("noaakey" = Sys.getenv("noaakey"))
alex_fips <- alex_nldas$fips
alex_fips <- unique(alex_fips)
alex_weather <- weather_fips(fips = alex_fips,
                             date_min = "2010-06-25",
                             date_max = "2010-07-02",
                             var = "PRCP")
```
